Light Transport Techniques for Tensor Field Visualization

### 2019-08-12 beamer2thesis/dummy.tex
upddate

\frame{
\frametitle{{Light Transport Gradient (LTG) - Isotropic field}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{itemize}
	\item Isotropic test field reveals offset response for the approach
	\bigskip
	\item natural shift against the inital light source (slice) direction (left)\\
%	$\Rightarrow$ initial light source configurations located close and pointing towards borders, are biased for low LTG (FTLE) responses
\end{itemize}
\end{small}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\caption*{\textit{Isotropic test field}}\bigskip
\begin{minipage}{.49\textwidth}
\includegraphics[height=\textwidth]{isotropic2.png} \caption*{a)~Glyphs}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[height=\textwidth]{iso_ftle.png} \caption*{b)~LTG($0^\circ$)}
\end{minipage}

\end{figure}

\end{column}
\end{columns}

>>>>

\frame{
\frametitle{{Transmission Profiles}}
{\small To interpret singular value systems of tensors as conductivity property for light transport, we will need transfer functions (transmission profiles) for the propagation scheme:}
\begin{block}{\centering \textbf{Ellipse Equation}}
\begin{align*}
	T(\omega) = \frac{ab}{\sqrt{a^{2}\sin^{2}(\omega-\varphi)+b^{2}\cos^{2}(\omega-\varphi)}} =\frac{\sigma_1\sigma_2}{\sqrt{\sigma_1^2\sin^2(\omega-\varphi)+\sigma_2^2\cos^2(\omega-\varphi)}}
\end{align*}
{\small with $\varphi=\mathop{atan2}(\sigma_{1,y},\sigma_{1,x})$ and $\sigma$: singular value, $a$: x-radius ellipse, $b$: y-radius ellipse}
\end{block}
$\Rightarrow$ transmission profiles $r(\omega)$ are defined as polar functions by the mapping of singular values to half-axes radii and the shift angle of the major singular vector $\varphi$

\frame{
\frametitle{{Related Work - Asymmetric Tensor Field Visualization}}

\begin{itemize}
	\item dual eigenvectors\footnote[frame]{Zheng and Pang ''2d asymmetric tensor analysis", 2005}: use complex conjugate eigenvectors as co-visualization for the complex domain along with ordinary eigenvectors to represent the real domain
	\bigskip
	\item pseudo eigenvectors\footnote[frame]{Laramee et al. ''2d asymmetric tensor field topology", 2012}: extension for dual eigenvectors to a full set or graph
	\bigskip
	\item scalar measures: tensor magnitude\footnote[frame]{Lin et al. ''Asymmetric tensor field visualization for surfaces", 2011}, tensor mode\footnote[frame]{Palacios et al. ''Feature surfaces in symmetric tensor fields based on eigenvalue
manifold", 2015}, isotropy index\footnote[frame]{see footnote 12}
\end{itemize}
